
\documentclass[aspectratio=1610]{beamer}
\usetheme{boxes}
\usecolortheme{crane}
\usepackage{amsmath,amsfonts}
\usepackage{algpseudocode}
\usepackage{multicol}



\begin{document}



% -------------------------------------------------------------
% Lesson 1
% -------------------------------------------------------------

\begin{frame}
\frametitle{Lesson 1. Problems and Exercises}
\LARGE
As a student you must accomplish one or many exercises or problems.\\~\\
\Large \alert{Problems}\\
Each lesson ends with one or more problems, more elaborate case studies which consists of several parts that lead the student through the steps required to arrive at a solution.
\\~\\ 
\Large \alert{Exercises} \\
Each section ends with exercises. Exercises are short questions, that test basic mastery of the material.
\end{frame}

% --------------------------------------------------------------
% Exercise 1 
% --------------------------------------------------------------
\begin{frame}{Lesson 1}{}
\begin{center}
\Huge Exercise 1
\end{center}
\end{frame}

\begin{frame}{Lesson 1, Exercise 1}{}
\Large
\textbf{Please answer the following questions:}\\~\\ 

\Large{
\begin{itemize}
    \item What are the main differences between IT and CS?
    \item Company X requires the installation of new software application on their network. Do they need to hire a specialist in IT or CS?
    \item You are trying to get a job in computer programming. But everyone is offering today a devops position. Are your CS skill valuable for this job? Explain that\\~\\
\end{itemize}}

Return in writing the answers by email, in text format or PDF
\end{frame}


\end{document}

